Online {\IterComp}

### 2017-09-16 related.tex
minor changes to related work

\subsection{{\IterComp}}
Multiple different adaptive compilation techniques have been proposed for finding a near optimal combination of optimization
settings~\cite{agakov06,hoste2008cole,kulkarni04,stephenson03} by probabilistically searching the space of possible combinations. But with
all of them there is uncertainty about whether the quality of their results depends on the data set used. Chen~\etal~\cite{chen10,chen12a}
examined this issue and showed that indeed the best optimization options differ across inputs. Still, in most cases it is possible to find
a combination of optimizations that produces good results across all inputs, by using a few tens of inputs to evaluate our optimizations
on. While a positive result, this is still impractical. Producing tens of realistic input sets might be difficult. Even if not, each
combination of optimization options has to be evaluated on every input set, increasing the time \itercomp takes by at least an order of
magnitude.

Recent research~\cite{chen12b,fang15} has used real data for performing online {\itercomp} on distributed data center applications. Each
worker receives a subset of the input dataset to evaluate a small set of optimization settings on. The best such setting from each round
is used for subsequent executions of the same code. By testing new settings and re-evaluating old ones on new datasets this approach makes
it more likely to select an optimization setting that works well across inputs. Like in~\cite{chen10} every setting is tested on the same
set of inputs, wasting time and energy. This approach only works well with MapReduce-like workloads, since it relies on the MapReduce
framework for repeating the same computation multiple times without side-effects or corrupting the input.

>>>>

\subsection{{\IterComp}}
Multiple adaptive compilation techniques have been proposed for finding a near optimal combination of optimization
settings~\cite{agakov06,hoste08,kulkarni04,stephenson03} by probabilistically searching the space of possible combinations. But with
all of them there is uncertainty about whether the quality of their results depends on the data set used. Chen~\etal~\cite{chen10,chen12a}
examined this issue and showed that indeed the best optimization options differ across inputs. Still, in most cases it is possible to find
an optimization sequence that produces good results across all inputs, by evaluating the optimizations on a representative set inputs.
While a positive result, this is still impractical. Producing a set of realistic inputs might be difficult. Even if not, each
optimization sequence has to be evaluated on every input, increasing the time \itercomp takes by at least an order of
magnitude.

Recent research~\cite{chen12b,fang15} has used real data for performing {\itercomp} on distributed data center applications. Each
worker receives a subset of the input dataset to evaluate a small set of optimization settings on. The best such setting from each round
is used for subsequent executions of the same code. By testing new settings and re-evaluating old ones on new datasets this approach makes
it more likely to select an optimization setting that works well across inputs. Like in~\cite{chen10} every setting is tested on the same
set of inputs, wasting time and energy. This approach only works well with MapReduce-like workloads, since it relies on the MapReduce
framework for repeating the same computation multiple times without side-effects or corrupting the input.
